### 2010-12-09 trunk/htdocs/user.tex
Keywords again
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1183 40876441-3496-0410-a613-a2fca35b2ae2
Try svn propset svn:keywords "Id HeadURL" user.tex
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1184 40876441-3496-0410-a613-a2fca35b2ae2
Back to just Id
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1186 40876441-3496-0410-a613-a2fca35b2ae2
Info on svnversion
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1194 40876441-3496-0410-a613-a2fca35b2ae2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  user.tex
%
%  The 'user' section which holds an overview, and discusses
%  compilation and running.
%
%  $Id: user.tex,v 1.2 2010-11-02 17:38:48 jlintuvu Exp $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2010 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\begin{verbatim}
$ make serial
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c d2q9.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c d3q15.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c d3q19.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c model.c
...
\end{verbatim}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  user.tex
%
%  The 'user' section which holds an overview, and discusses
%  compilation and running.
%
%  $Id$
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2010 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The other thing required by the Makefile is the utility
\texttt{svnversion}, which allows the compile-time SVN version number to
be included in the executable (and hence the output of the program). This
is useful to remember which version you were using when looking at
results at a later date. If
\texttt{svnversion} is not available (and it
should be if you have downloaded the code via SVN), you may get an
error message, but the code should still compile.

@@

\begin{verbatim}
$ make serial
gcc  -D SVN_REVISION='"'`svnversion`'"' -c svn.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c d2q9.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c d3q15.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c d3q19.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c model.c
...
\end{verbatim}
